No publication without preservation: the argument against web-based tools in genomics

### 2023-12-02 manuscript/letter.Rmd
update with data retention mandates

Therefore, we caution against using data from web-based tools for publication, unless there is a system in place to enable future reproducibility.
Scripted workflows are perhaps the most suitable solution for fostering long-term reproduction, but require expertise in computer programming.
We have written a protocol for extremely reproducible enrichment analysis in R, designed for novice bioinformaticians to fill in this gap [@Ziemann2023-kz], but we understand this isn't for everyone.
ShinyGO is another potential remedy, as it provides most of the necessary features in a point-and-click web interface but also allows users to download all historical versions of the tool to be run as
a Docker based web page on the users own hardware [@Ge2020-qe].
In order to get genomics research to meet the ten-year reproducibility challenge [@Perkel2020-io], we need progress towards better tooling, a greater emphasis on investigator training, institutional support,
funder mandates, stronger publication criteria, and more incentives for rigourous and reliable practices [@Lewis2016-qh; @Diong2021-ma].

>>>>

Researchers should keep in mind that institutional and funding mandates for data retention also apply to software and algorithms [@NHMRC2019-wu ; @Harvard_2023-cl].
Therefore, to remain compliant with these mandates and support reproducibility, we caution against using data from web-based tools for publication unless there is a system in place to enable future reproducibility.
Scripted workflows are perhaps the most suitable solution for enabling reproduction in the long-term, but require expertise in computer programming.
We have written a protocol for extremely reproducible enrichment analysis in R, designed for novice bioinformaticians to fill in this gap [@Ziemann2023-kz], but we understand this isn't for everyone.
ShinyGO is another potential remedy, as it provides most of the necessary features in a point-and-click web interface but also allows users to download all historical versions of the tool to be run as
a Docker based web page on the users own hardware [@Ge2020-qe].
In order to get genomics research to meet the ten-year reproducibility challenge [@Perkel2020-io], we need progress towards better tooling, a greater emphasis on investigator training, institutional support,
funder mandates, stronger publication criteria, and more incentives for rigourous and reliable practices [@Lewis2016-qh; @Diong2021-ma].
